Teaching a Class to Grade Itself using Game Theory

### 2013-09-21 Primes Write up.tex
Edited to near perfection

\documentclass[12pt, Arial]{article}   	
\title{Teaching a Class to Grade Itself using Game Theory}
\author{Nick Kaashoek and William Wu}
\date{\today}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{wrapfig}
\usepackage[section]{placeins}
\usepackage{enumitem}
\setlength{\parindent}{15pt}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole. Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started in May of 2012~\cite{canmoocsreducecc}. However, the MOOC's main importance comes from its scalability. MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: By the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

High student-professor ratios lead to problems for professors. Professors are simply unable to grade hundreds of thousands of submissions. Currently, two types of solutions are used to remedy the problem: automated grading and peer grading. Automated grading relies on machines to grade assignments. However, machines can only check certain types of answers (i.e. multiple choice), severely limiting the depth of the questions asked~\cite{rightandwrongmoocs}. Even though automated grading for written essays is an active area of research with much recent progress, a usable solution does not yet exist~\cite{automatedsystemssuck}. On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofmoocs}. Although both of these systems are interesting concepts, they are limiting or inaccurate in practice~\cite{howaccurateispeergrading}.

The problem of grading large numbers of submissions is important to solve. Without a solid solution, MOOCs cannot provide efficient feedback for their students, rendering them unable to effectively evaluate their knowledge. Because this limits their learning abilities, it is imperative to create an efficient system that enables students to receive feedback to learn efficiently.

@@

Game theory allows the creation of a unified system of assumptions that simulate student behavior in a class. The grading system can be viewed as a ``game'' where the set of ``rules'' are known to everyone and the ``players'' --- the students --- ``play'' the game in order to get the best possible result. Using the assumptions and rules, game theory can predict how students will behave when they ``play''. This way, mechanism efficiency and effectiveness cam be proved, allowing the evaluation of different sets of rules.

@@

This research opportunity is made interesting by the complexity of human nature as well as its necessity for practical use. This paper will cover the thought process of mechanisms leading up to the final mechanism of grading, as well as explain the final mechanism and its implications. All mechanisms and related calculations will be presented. Section 2 describes the mathematical definition of the problem as well as its rules and assumptions.

\section{Materials and Methods}
\subsection{The Scenario}
In our trying to find a solution to the professor's problem, we consider the case of a single assignment. To apply them to an entire class, simply apply them to each assignment. In such a ``round''of grading, there are $n$ students, who each bring one ungraded paper to the professor. These ungraded papers are like the input for a function. Each of these papers, $i$ has an objective score $o_i\mid 0<o_i<100$. This is the score the professor would give out. Our mechanism then has the students grade the papers in a clever way and output the grades. We identify the students by an index $i$ from $1$ to $n$ and the professor as index $0$.
\subsection{Assumptions}
To create the models that are used to predict the behavior of the students, we use a set process every each time. To begin with, we create a set of assumptions. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model. The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side. To begin with, a simple set of assumptions was created:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item Students want good grades
 	\item Doing work makes students unhappy
  	\item Students want to be happy
 	\item Students only care about their final happiness
  	\item The happiness of a student is only affected by their grade and the amount of work they do
\end{enumerate}
However, we wanted to create a mathematical solution, so these assumptions need to be changed into math terms. The result of this is as follows:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
  \item Students can grade others' work accurately (i.e they can find $o_i$) but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
  \item Students want to maximize their final happiness, expressed as $H(g)-W$
  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting x and y each with 50 percent chance, gives a happiness of 7.5).
  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It doesn't depend on the score of others
\end{enumerate}

\paragraph{Why?}
There are two questions that need to be addressed, first, why is happiness important, and second, why are the scores of others not important? Happiness is important because it provides a measure of the combination of the work performed and grade received. The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness, for example, in a coursera course with 150,000 students, it is extremely unlikely that any student will ever be able to have any effect on the grade of another student. So, for simplicity, we ignore the ``friendship''effect.
\subsection{First major objective}
The first goal of the system is to make sure that every student gets the most happiness when they correctly grade every assignment that the professor asks them to. If a system has this property, then it is reasonable to assume that students will always choose to grade every assignment the professor asks them to. Without this property, a system becomes extremely unpredictable. So, in other words, no student can deviate from the truthful strategy to improve his happiness. In math terms, if by acting honestly student i grades $w_i$ papers and gets a grade of $g_i$ there shouldn't be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.

\subsection{Benchmark}
%Efficiency objective%
The next step is to create a system that will allow multiple different mechanisms to be compared and evaluated side by side; in other words, a benchmark needs to be created. To do this, two things need to be addressed: how accurate the grades the mechanism produces are, and how happy people are. Because happiness can be directly expressed as a function of work, the two things that need to be evaluated are how accurate the grades are, and how much work is being done. As such, the benchmark becomes a sum of the amount of work done by the person doing the most work and the maximum deviation from the correct grades; the lower the sum, the more efficient the mechanism. In mathematical terms we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.

When creating this benchmark, there are 2 things that need to be considered. First of all, caring about accuracy. This is important because if we don't care, then we could give everyone a 100, which, as explained earlier, is a terrible mechanism. Secondly, caring about work done. If we don't care about the amount of work done, we could have the professor grade everything, which is bad because it makes the professor extremely unhappy.

@@

\subsection{The Calibration Mechanism}

\subsubsection{Mechanism}
First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we used as a starting point.
\begin{definition}(Calibration Mechanism)
In this mechanism, the professor chooses one paper to grade, which he gives to every student, along with a second, ungraded paper. If the students fail to grade the paper the professor graded correctly, they get a 0. Otherwise they get the minimum of an arbitrary number $???$ and the grade their assigned grade.
\end{definition}
\begin{theorem}
With this mechanism, all students should behave honestly and the mechanism shoul output accurate grades while maintaining a low amount of per-person work.
\end{theorem}
\begin{proof}[Why this works]
See figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.

G is the maximum of \{ some minimum value, the assigned grade \}.
The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.

@@

This means that if $H(G) - 2 > H(0)$, then student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, $H(???) > H(0) + 2$.
The teacher expends one unit of effort, each student spends 2, as long as the teacher set the minimum value high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
So, maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
\end{proof}
\subsubsection{Benchmark}
The means that the value of the objective function in this case is 4, a very low value, because it is exactly the same as if we convinced every student to grade accurately grade 4 papers.

\subsubsection{Problems}
This mechanism is extremely simple, and relies on the unrealistic assumption that students are unable to communicate with each other. If they were able to, students would be able to figure out which paper is calibrated by checking which one they all share.

\subsection{Improved Calibration Mechanism}
\subsubsection{The Mechanism}
In the calibration mechanism, we assumed that students couldn't communicate with each other. For this mechanism, we relax this assumption, thus changing assumption number 11, which now reads as: \emph{All students are able to communicate with each other}
\begin{definition}(Improved Calibration Mechanism)
In this mechanism, we apply the calibration mechanism on a larger scale. Every student grades the papers of \emph{k} other students. The professor also grades every \emph{kth} paper, these are the calibrated papers. The same system for assigning grades is used as in the calibration mechanism.
\end{definition}
\begin{theorem}
In this mechanism, students will return accurate grades, even though they can communicate with each other.
\end{theorem}
\begin{proof}
In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other. As such, there are 3 options for the students. They can grade 0 papers, giving them a happiness of $H(0) = 0$ or grade all the papers they are assigned, giving them a happiness of $H(g) - k$ or they can grade $i$ papers giving them a happiness of $\frac{i}{k} \cdot H(G)-i$. This means that it is always worse to grade i, because happiness from grading i is equal to i times happiness for grading 0 plus i-k times happiness for grading k.

Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers. As long as the minimum value is high enough, the papers will be accurately graded, as before.
\end{proof}
\subsubsection{Benchmark and Problems}
The maximum amount of work will be done by the professor, who has to grade $\frac{n}{k}$ papers, making the benchmark $\frac{n}{k}+4$, a potentially higher value than before. The huge problem with this is the high amount of work being done.

\subsection{The Deduction Mechanism}
With this mechanism, we aim to fix the faults of the previous mechanism while retaining the same set of assumptions. Other than reducing the workload, we aim to accomplish the same goals as the improved calibration mechanism.
\subsubsection{Mechanism}
See figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.
\begin{definition}(Deduction Mechanism)
In this mechanism, each paper is randomly assigned to 2 students. Students deduct as many points as they want, and write a justification for each of them. For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, sudent $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and j receives $\frac{x_j}{x_i + x_j}$. Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives an incorrect grader a 0. To compute the final score for a student, their final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to $H(g)$. (Then the student’s grade is converted from Happiness to an actual score).
\end{definition}
\begin{theorem}
The addition of the contribution score being added or subtraced should encourage graders to honestly grade papers, for fear of losing points and the possible reward.
\end{theorem}
\begin{proof}
The graders have two choices, they can either grade the papers, or not grade them.

@@

Therefore, it is in everyone's best interest to honestly grade the paper.
\end{proof}
\subsection{Final Assumptions}
Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view, however, the deduction mechanism still has some unrealistic parts, primarily the inablitity to deal with students who are incompetent graders. With this in mind, we designed a final set of assumptions that more effectively simulate a realistic world.

\begin{enumerate}[itemsep=0pt, parsep=0pt]
\item When grading, $w_i=0 \oplus w_i=1$
\item For all students, $g_i \neq o_i$
\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral.
\item For a given student in $N$, that student has contact with all other students in $N$.
\end{enumerate}
% Put simply:
% \begin{enumerate}[itemsep=0pt, parsep=0pt]
% \item Students cannot ``half bake''an assignment
% \item Students can't always get the exact objective score
% \item Students want good grades
% \item Students don't like grading
% \item Students are selfish
% \item Doing work costs 1 unit of effort
% \item Students are risk neutral with respect to happiness
% \item All students can talk to each other
% \end{enumerate}
\newpage
\section{Illustrations}
\begin{figure}[!ht]
	\centering
		\includegraphics[width=0.9\textwidth]{Comparison.eps}
		\caption {A comparison of mechanisms in terms of scalability, workload, and objective function.}
		\vspace{-100pt}
		\label{fig:Comparisongraph}
\end{figure}
\begin{figure}[!ht]
	\centering
		\includegraphics[width=0.75\textwidth]{Flowchart-Calibration.eps}
		\caption {A flowchart of the Calibration Mechanism from the student perspective.}
		\label{fig:calibration}
\end{figure}
\begin{figure}[!ht]
	\centering
		\includegraphics[width=0.75\textwidth]{Flowchart-Deduction.eps}
		\caption {A flowchart of the Deduction Mechanism from the student perspective.}
		\label{fig:deduction}
\end{figure}
\section{Discussion}
With this research, the goal was to create a mechanism that fulfilled our two goals; incentivizing students to play the ``game''the way they were meant to, and to efficiently and effectively grade the assignments of these students. Although our mechanisms are not truly realistic, the significance of them cannot be denied. The mechanisms created by the end of the research came very close to realism, with only one factor missing, and could still be implemented in a classroom environment where all students are capable of grading others assignments efficiently.

@@

Also, by taking the happiness of the students into account, it can be almost guaranteed that these mechanisms are better for the students than automated grading, or any other solutions attempted before. Many of the complaints that students give out include something along the lines of the fact that they cannot give feedback on their feedback, a problem in the Coursera system~\cite{theproblemswithpeergradingincoursera}. This problem is fixed in our mechanism by allowing the students to appeal their grades and to have multiple rounds of grading. Other commonly expressed problems such as the variability of feedback are also addressed by these mechanisms, which prevent this from happening by having a rigid set of justifications required. This means that students cannot simply pass on a paper with the word ``good,''they must rather take the time to explain why they took off any points they did, or why they gave the paper a perfect score.

Besides making the students happier than they are in other peer grading systems, the mechanisms that result from this research also provide more accurate and legitimate grades for the students. In current peer grading schemes, it is easy for students to just ``game''the system and fake their way through a course. Giving anonymous feedback, for example, does not encourage students to be honest, rather, it gives them a reason to be \emph{dis}honest~\cite{theproblemswithpeergradingincoursera}. This allows students to dishonestly grade the work of others, as well as just give whomever they want a better grade than that person actually deserves. In our mechanisms, however, these problems are solved by removing anonymity and adding incentives to make students behave honestly, no matter who they are grading.

>>>>

\documentclass[12pt, Arial]{article}   	
\title{Teaching a Class to Grade Itself using Game Theory}
\author{}%Nick Kaashoek and William Wu
\date{}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{amsthm}
\usepackage{wrapfig}
\usepackage[section]{placeins}
\usepackage{enumitem}
\setlength{\parindent}{15pt}
\newtheorem{theorem}{Theorem}
\newtheorem{definition}{Definition}
\begin{document}
\maketitle
\section{Introduction}
Over the past few years, there has been a tremendous increase in the popularity of MOOCs (Massive Open Online Courses), as well the importance of MOOCs to education as a whole. Popular MOOC systems such as Coursera or EdX are well funded, which explains their rapid growth: 60 million dollars were invested in EdX when it started in May of 2012~\cite{canmoocsreducecc}. However, the MOOC's main importance comes from its scalability. MOOCs are able to educate massive numbers of students from anywhere in the world~\cite{makingsenseofmoocs}: By the end of 2012, 1.7 million students had attended a course through Coursera~\cite{swotanalysisofmoocs}. The sheer number of students leads to high student-professor ratios that can reach 150,000:1 in some courses.

High student-professor ratios lead to problems for professors. Professors are simply unable to grade hundreds of thousands of submissions. Currently, two types of solutions are used to remedy the problem: automated grading and peer grading. Automated grading relies on machines to grade assignments. However, machines can only check certain types of answers (i.e. multiple choice), severely limiting the depth of the questions asked~\cite{rightandwrongmoocs}. Even though automated grading for written essays is an active area of research with much recent progress, but the quality and accuracy of such systems is under heavy debate~\cite{automatedsystemssuck}. On the other hand, peer grading can grade any type of question, but a system utilizing it could easily be ``hacked'' by the students~\cite{makingsenseofmoocs}. Although both of these systems are interesting concepts, they are limiting or inaccurate in practice~\cite{howaccurateispeergrading}.

The problem of grading large numbers of submissions is important to solve. Without a solid solution, MOOCs cannot provide efficient feedback for students taking them. This renders the students unable to effectively evaluate the mastery of the course material. Therefore, it is imperative to create an efficient system that enables students to receive feedback to learn effectively.

@@

Game theory allows the creation of a unified system of assumptions that simulate student behavior in a class. The grading system can be viewed as a ``game'' where the set of ``rules'' are known to everyone and the ``players'' --- the students --- ``play'' the game in order to get the best possible result. Using the assumptions and rules, game theory can predict how students will behave when they ``play''. This way, mechanism efficiency and effectiveness can be proved, allowing the evaluation of different sets of rules.

@@

This research opportunity is made interesting by the complexity of human nature as well as its huge practical value. This paper will cover the thought process of mechanisms leading up to the final mechanism and its implications. All mechanisms and related calculations will be compared in terms of scalability and effectiveness.

\section{Materials and Methods}
\subsection{The Scenario}
The first step to remedy the professor's problem is to follow the grading of a single assignment. The assignment is easy enough to consider independently, and can be generalized to multiple assignments. In such a ``round'' of grading, there are $n$ students, who each bring one ungraded paper to the professor. These ungraded papers are like the input for a function. Each of these papers, $i$ has an objective score $o_i\mid 0<o_i<100$. This is the score the professor would give out. Our mechanism then has the students grade the papers in a clever way and output the grades. We identify the students by an index $i$ from $1$ to $n$ and the professor as index $0$.
\subsection{Assumptions}
To create the models that are used to predict the behavior of the students, we use a set process every each time. To begin with, we create a set of assumptions. These assumptions are used to explain how students will act in a given situation; for example, one assumption could be that students want good grades. This is a logical assumption that is likely true, as all the assumptions are, and can be used to classify the behavior of the students in a model. The same set of assumptions can be used for multiple models, which will allow us to evaluate different models side by side. To begin with, a simple set of assumptions was created:
\begin{enumerate}[itemsep=0pt, parsep=0pt]
	\item Students want good grades
 	\item Doing work makes students unhappy
  	\item Students want to be happy
 	\item Students only care about their final happiness
  	\item The happiness of a student is only affected by their grade and the amount of work they do
\end{enumerate}
To re-express the above in mathematics:
\begin{enumerate}
  \item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
  \item Students can grade others' work accurately (i.e they can find $o_i$) but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
  \item Students want to maximize their final happiness, expressed as $H(g)-W$
  \item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral (i.e, if $H(x)=10$ and $H(y)=5$, then getting x and y each with 50 percent chance, gives a happiness of 7.5).
  \item The final happiness depends only on the grade assigned to the student and the amount of effort exercised. It doesn't depend on the score of others
\end{enumerate}

There are two things that need to be considered: the importance of a student's own happiness and the irrelevance of others' grades. Happiness is important because it provides a measure of the combination of the work performed and grade received. The reasoning for not caring about friends is due to the relatively low impact they have on someone's grades and happiness, for example, in a Coursera course with 150,000 students~\cite{swotanalysisofmoocs}, it is extremely unlikely that any student will ever be able to have any effect on the grade of another student. So, for simplicity, we ignore the ``friendship''effect.
\subsection{First major objective}
The first goal of the system is to make sure that every student gets the most happiness when they correctly grade every assignment that the professor asks them to. If a system has this property, then it is reasonable to assume that students will always choose to grade every assignment the professor asks them to. Without this property, a system becomes extremely unpredictable. So, in other words, no student can deviate from the truthful strategy to improve his happiness. In math terms, if by acting honestly student i grades $w_i$ papers and gets a grade of $g_i$ there shouldn't be any way for the student to spend $w'_i$ units of effort and get a score $g'_i$ where $H(g'_i)-w'_i > H(g_i)-w_i$.

\subsection{Benchmark}
%Efficiency objective%
A benchmark that will allow different mechanisms to be compared is vital to the iterative process of mechanism development. Mechanisms should be compared in terms of the relative happiness of people --- which can be expressed as a function of work done --- as well as the accuracy of the grades produced. Therefore, the benchmark becomes the maximum work assigned to any student plus the maximum deviation of student assigned grades to the correct grades, so that a lower scoring mechanism produces a more desired outcome. In mathematical terms, we want to minimize the function $max_{i \ge 1} |H(g_i)-H(o_i)| + max_{i \ge 0} w_i$ in the worst possible case.

When creating this benchmark, there are 2 things that need to be considered: accuracy and workload. Accuracy is important because if we don't care, then we could give everyone a 100, which, as explained earlier, is a terrible mechanism. Secondly, caring about work done. If we don't care about the amount of work done, we could have the professor grade everything, which is bad because it makes the professor extremely unhappy.

@@

\subsection{The Calibration Mechanism}
\label{sec:calibration}

\subsubsection{Process}
First, we design a mechanism that does extremely well in a model defined by our simple and unrealistic assumptions, which we used as a starting point.
\begin{definition}(Calibration Mechanism)
In this mechanism, the professor chooses one paper to grade, which he gives to every student, along with a second, ungraded paper. If the students fail to grade the paper the professor graded correctly, they get a 0. Otherwise they get the minimum of an arbitrary number $???$ and the grade their assigned grade.
\end{definition}
\begin{theorem}
With this mechanism, all students should behave honestly and the mechanism shoul output accurate grades while maintaining a low amount of per-person work.
\end{theorem}

\begin{proof}[Analysis]
G is the maximum of \{ some minimum value, the assigned grade \}.
The happiness of one student grading one paper is equivalent to $\frac{H(G)+H(0)}{2}-1$ Because the students have a 0.5 chance of getting a 0, and a one-half chance of getting G.

@@

This means that if $H(G) - 2 > H(0)$, then student will grade both papers. So, for the professor to guarantee that the students use effort and obtain the correct grades, $H(???) > H(0) + 2$.
The teacher expends one unit of effort, each student spends 2, as long as the teacher set the minimum value high enough.
Everything above $H^{-1}(2)$ will be graded correctly, while everything below it will receive a score of $H^{-1}(2)$.
So, maximum deviation is $H^{-1}(2)$, because this is the score that might be given to someone who deserves a 0. Expressed in happiness units, the value is 2.
\end{proof}
\emph{This process is summarized in figure~\ref{fig:calibration} on page~\pageref{fig:calibration}.}

\subsubsection{Benchmark and Remaining Issues}
The means that the value of the objective function in this case is 4, a very low value, because it is exactly the same as if we convinced every student to grade accurately grade 4 papers.

\emph{The benchmark results for The Calibration Mechanism can be seen in figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}

This mechanism is extremely simple, and relies on the unrealistic assumption that students are unable to communicate with each other. If they were able to, students would be able to figure out which paper is calibrated by checking which one they all share.

\subsection{Improved Calibration Mechanism}
\subsubsection{Process}
In the calibration mechanism, we assumed that students couldn't communicate with each other. For this mechanism, we relax this assumption, thus changing assumption number 11, which now reads as: \emph{All students are able to communicate with each other}
\begin{definition}(Improved Calibration Mechanism)
In this mechanism, we apply the calibration mechanism on a larger scale. Every student grades the papers of \emph{k} other students. The professor also grades every \emph{kth} paper, these are the calibrated papers. The same system for assigning grades is used as in the calibration mechanism.
\end{definition}
\begin{theorem}
In this mechanism, students will return accurate grades, even though they can communicate with each other.
\end{theorem}
\begin{proof}[Analysis]
In this scheme, because of the overlapping papers, the students have no better way of figuring out which papers are calibrated than random guessing, even though they can all communicate with each other. As such, there are 3 options for the students. They can grade 0 papers, giving them a happiness of $H(0) = 0$ or grade all the papers they are assigned, giving them a happiness of $H(g) - k$ or they can grade $i$ papers giving them a happiness of $\frac{i}{k} \cdot H(G)-i$. This means that it is always worse to grade i, because happiness from grading i is equal to i times happiness for grading 0 plus i-k times happiness for grading k.

Even though the students can communicate with one another, they will have no way to determine which paper is calibrated because there are multiple calibrated papers that overlap, and are thus best off grading all the papers. As long as the minimum value is high enough, the papers will be accurately graded, as before.
\end{proof}
\subsubsection{Benchmark and Remaining Issues}
The maximum amount of work will be done by the professor, who has to grade $\frac{n}{k}$ papers, making the benchmark $\frac{n}{k}+4$, a potentially higher value than before. The huge problem with this is the high amount of work being done.

\emph{The benchmark results for The Improved Calibration Mechanism can be seen in figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}

\subsection{The Deduction Mechanism}
\label{sec:deduction}
With this mechanism, we aim to fix the faults of the previous mechanism while retaining the same set of assumptions. Other than reducing the workload, we aim to accomplish the same goals as the improved calibration mechanism.
\subsubsection{Process}
\begin{definition}(Deduction Mechanism)
In this mechanism, each paper is randomly assigned to 2 students. Students deduct as many points as they want, and write a justification for each of them. For each paper graded by students $i$ and $j$, where $i$ took of $x_i$ points and $j$ took off $x_j$, sudent $i$ receives contribution score $\frac{x_i}{x_i + x_j}$, and j receives $\frac{x_j}{x_i + x_j}$. Students may then choose to appeal their paper's grade if they are unhappy with it, at which point the professor grades it and gives an incorrect grader a 0. To compute the final score for a student, their final grade on the assignment is calculated as follows: 4 points times their contribution score are added or subtracted to $H(g)$. (Then the student’s grade is converted from Happiness to an actual score).
\end{definition}
\begin{theorem}
The addition of the contribution score being added or subtraced should encourage graders to honestly grade papers, for fear of losing points and the possible reward.
\end{theorem}
\begin{proof}[Analysis]
The graders have two choices, they can either grade the papers, or not grade them.

@@

Therefore, it is in everyone's best interest to honestly grade the paper.

\end{proof}
\emph{This process is summarized in figure~\ref{fig:deduction} on page~\pageref{fig:deduction}.}

\emph{The benchmark results for The Calibration Mechanism can be seen in figure~\ref{fig:comparison} on page~\pageref{fig:comparison}.}

\subsection{Final Assumptions}
Now that we have reached a point far into the research, we have a model that accounts for a very realistic world view, however, the deduction mechanism still has some unrealistic parts, primarily the inablitity to deal with students who are incompetent graders. With this in mind, we designed a final set of assumptions that more effectively simulate a realistic world.

\begin{enumerate}[itemsep=0pt, parsep=0pt]
\item When grading, $w_i=0 \oplus w_i=1$
\item For all students, $g_i \neq o_i$
\item Students all share a common happiness function, $H(g)$, where \emph{g} represents the grade the students received, and the output is their happiness. w.l.o.g. $H(0)=0$
\item Students can grade others' work perfectly but doing so costs one unit of happiness. Therefore after grading $W$ papers, a student's happiness can be expressed as $H(g)-W$
\item Final happiness is unaffected by other people, only affected by $g_i$ and $w_i$
\item Doing work costs one unit of happiness, so after grading a paper, a student's happiness can be expressed as $H(g)-W$,W is number of work units used
\item Students only care about the expectation of their final happiness, which, put in game theory terms, makes them risk neutral.
\item For a given student in $N$, that student has contact with all other students in $N$.
\end{enumerate}
\section{Illustrations}
{
\noindent
\begin{figure}[!h]
	\centering
		\includegraphics[width=\textwidth]{Comparison.eps}
		\caption {A comparison of mechanisms in terms of effectiveness and scalability.\label{fig:comparison}}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=\textwidth]{Flowchart-Calibration.eps}
		\caption {A flowchart of the Calibration Mechanism (section~\ref{sec:calibration}, page~\pageref{sec:calibration}) from the student perspective.\label{fig:calibration}}
\end{figure}
\begin{figure}
	\centering
		\includegraphics[width=\textwidth]{Flowchart-Deduction.eps}
		\caption {A flowchart of the Deduction Mechanism (section~\ref{sec:deduction}, page~\pageref{sec:deduction}) from the student perspective.\label{fig:deduction}}
\end{figure}
}
\section{Discussion}
With this research, the goal was to create a mechanism that fulfilled our two goals; incentivizing students to play the ``game''the way they were meant to, and to efficiently and effectively grade the assignments of these students. Although our mechanisms are not truly realistic, the significance of them cannot be denied. The mechanisms created by the end of the research came very close to realism, with only one factor missing, and could still be implemented in a classroom environment where all students are capable of grading others assignments efficiently.

@@

Also, by taking the happiness of the students into account, it can be almost guaranteed that these mechanisms are better for the students than automated grading, or any other solutions attempted before. Many of the complaints that students give out include something along the lines of the fact that they cannot give feedback on their feedback, a problem in the Coursera system~\cite{howaccurateispeergrading}. This problem is fixed in our mechanism by allowing the students to appeal their grades and to have multiple rounds of grading. Other commonly expressed problems such as the variability of feedback are also addressed by these mechanisms, which prevent this from happening by having a rigid set of justifications required. This means that students cannot simply pass on a paper with the word ``good,''they must rather take the time to explain why they took off any points they did, or why they gave the paper a perfect score.

Besides making the students happier than they are in other peer grading systems, the mechanisms that result from this research also provide more accurate and legitimate grades for the students. In current peer grading schemes, it is easy for students to just ``game''the system and fake their way through a course. Giving anonymous feedback, for example, does not encourage students to be honest, rather, it gives them a reason to be \emph{dis}honest~\cite{howaccurateispeergrading}. This allows students to dishonestly grade the work of others, as well as just give whomever they want a better grade than that person actually deserves. In our mechanisms, however, these problems are solved by removing anonymity and adding incentives to make students behave honestly, no matter who they are grading.
